A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-08-19 tex/paper.tex
gl51 fix logg

%Given the apparent differences in the quoted precisions, it is beneficial to review what factors 
%into the parameter uncertainties.  In our approach, we consider contributions from both trivial 
%(Poisson) noise and a non-trivial Gaussian process covariance matrix.\footnote{It is worth noting 
%that the {\sc CfA/Kurucz} library is so good for stars like WASP-14 over this limited spectral 
%range that no local covariance kernels need to be instantiated; in this specific case we use only a 
%global covariance kernel.}  To break down their respective contributions, we performed the 
%same analysis with only a trivial covariance matrix ($b = 1$; $\cov = 0$), which simplifies the 
%likelihood function to the familiar $\chi^2$ form.  Doing this, we identify little bias to the 
%best-fit parameters, but find unrealistic precision (i.e., $T_{\rm eff}$ to $\pm$5\,K, 
%$[{\rm Fe/H}]$ to $\pm0.004$\,dex, and $v \sin i$ to $\pm0.01$\,km s$^{-1}$).  Such small 
%uncertainties are to be expected, since the prescribed likelihood function presumes that the data 
%are generated from the model; in this paradigm, the only way to introduce deviation is through 
%white noise.  Of course, that implicit assumption is invalid, since just a few simple parameters 
%($\vT$) are generally insufficient to perfectly account for the thousands of pixels and hundreds of 
%spectral features in a typical dataset.  In essence, the data and an imperfect model spectrum also 
%have {\it systematic} differences that contribute to the uncertainties (in addition to the Poisson 
%noise), which we forward-model using a non-trivial covariance matrix.  In this specific case, these 
%systematic uncertainties and the Poisson uncertainties contribute roughly equally to the $\vT$
%posteriors.

>>>>

Given the apparent differences in the quoted precisions, it is beneficial to review what factors 
into the parameter uncertainties.  In our approach, we consider contributions from both trivial 
(Poisson) noise and a non-trivial Gaussian process covariance matrix.\footnote{It is worth noting 
that the {\sc CfA/Kurucz} library is so good for stars like WASP-14 over this limited spectral 
range that no local covariance kernels need to be instantiated; in this specific case we use only a 
global covariance kernel.}  To break down their respective contributions, we performed the 
same analysis with only a trivial covariance matrix ($b = 1$; $\cov = 0$), which simplifies the 
likelihood function to the familiar $\chi^2$ form.  Doing this, we identify little bias to the 
best-fit parameters, but find unrealistic precision (i.e., $T_{\rm eff}$ to $\pm$5\,K, 
$[{\rm Fe/H}]$ to $\pm0.004$\,dex, and $v \sin i$ to $\pm0.01$\,km s$^{-1}$).  Such small 
uncertainties are to be expected, since the prescribed likelihood function presumes that the data 
are generated from the model; in this paradigm, the only way to introduce deviation is through 
white noise.  Of course, that implicit assumption is invalid, since just a few simple parameters 
($\vT$) are generally insufficient to perfectly account for the thousands of pixels and hundreds of 
spectral features in a typical dataset.  In essence, the data and an imperfect model spectrum also 
have {\it systematic} differences that contribute to the uncertainties (in addition to the Poisson 
noise), which we forward-model using a non-trivial covariance matrix.  In this specific case, these 
systematic uncertainties and the Poisson uncertainties contribute roughly equally to the $\vT$
posteriors.
